---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
set.seed(0)
```

# vecvec

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/vecvec)](https://CRAN.R-project.org/package=vecvec)
<!-- badges: end -->

The vecvec package allows you to create vectors of mixed classes. It works similarly to `factor()`, in which the values of a vector (levels of a factor) are stored in the attributes. This also allows for efficient computation when the values are replicated, since operations apply to the unique values of the vector.

## Installation

You can install the development version of vecvec like so:

``` r
remotes::install_github("mitchelloharawild/vecvec")
```

## Example

Use `new_vecvec()` to create a vecvec. Here we combine three vectors of different types.

```{r construction}
library(vecvec)

x <- new_vecvec(Sys.Date(), Sys.time(), rnorm(10))
x
```

Internally, the vectors are stored separately in the attributes.

```{r internals}
str(x)
```

Operations apply to all vector types.

```{r arith}
x + 1
```

When subsetting, unused values are dropped.

```{r subset}
x[1]
str(x[1])
```

When a vecvec is replicated, only the indexing is replicated.

```{r replicated}
str(rep(x, each = 10))
str(x[c(1,1,1,3,2,2)])
```

The values in the attribute are unchanged, which allows for efficient computation since operations apply to the attributes (which are not replicated).

```{r efficient}
str(rep(x, each = 10) + 100)
```

If the arguments is differ across replicated indices, the resulting vecvec is [*expanded*](https://github.com/mitchelloharawild/vecvec/issues/2)

```{r expansion}
str(rep(x, each = 10) + 1:120)
```

